Survey of Misuses of the Kolmogorov–Smirnov-Test

### 2022-04-01 Manuscript/manuscript.tex
incomplete literature review in the introduction, added sources

However, the test is often misused. The standard one-sample K-S test applies to independent, continuous data with a hypothesized distribution that is completely specified. Often in literature, it has been "discovered" that the test loses its power when applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters. For instance in \citet{Steinskog}, the authors demonstrate the change in power when using estimated parameters and stress caution when using the K-S test in such ways. The purpose of this paper is to expand on the misuses of the K-S test and propose solutions in the case that the K-S test would still like to be used.

In order to set up the demonstrations, simulated data is used throughout. Unless otherwise specified, the random data is generated from a standard normal distribution with sample size $100$. Therefore the cumulative distribution $F(x)$ of the K-S test is standard normal.

@@

The K-S test shows significant issues in the case of fitted parameters. As previously mentioned, one assumption of the K-S test is that the hypothesized distribution is completely specified. However, the procedure is sometimes performed where the population cumulative distribution $F(x)$ has parameters $\mu=\Xbar$, the sample mean, and $\sigma^2=s^2$, the sample variance \citep{Lilliefors}. \citet{Lilliefors} shows that using the standard table when values of the mean and standard deviation are estimated obtains extremely conservative results. \citet{Capasso} concludes that failing to re-estimate the parameters may lead to wrong, overly-conservative approximations to the distributions of goodness-of-fit test statistics based on the empirical distribution function. \citet{Capasso} also notes that the impact of this possible mistake may turn out to be dramatic and does not vanish as the sample size increases. This case is demonstrated in Figure~\ref{fig:hist_fitted} under the Naive plot. The naive K-S test was performed by estimating the parameters of $F(x)$ using the fitted distribution of the sample data. Since the data is generated from a standard normal distribution with seemingly all assumptions met, a uniform distribution of $U(0,1)$ is expected for the p-values. However this is under the assumption that the K-S test holds its power, which it no longer does due to using fitted parameters. Therefore, there is notable deviation from the uniform distribution.

To resolve this problem, both parametric and non-parametric bootstrap can be performed. Performing bootstrap onto goodness-of-fit tests such as the K-S test is a well-researched topic. \citet{Genest} provides validity for using parametric bootstrap with various goodness-of-fit tests. \citet{Babu} details the bootstrap procedure for goodness-of-fit tests and notes that both parametric and non-parametric procedures lead to correct asymptotic levels, however there is a correction required for the non-parametric case.

@@

\citet{Steinskog}
\citet{Weiss}
\citet{Massey}
\citet{Lilliefors}
\citet{Arnold}
\citet{Conover}
\citet{Gleser}
\citet{Babu}
\citet{Butorina}
\citet{Racine}
\citet{Wang}
\citet{Capasso}
\citet{Dimitrova}
\citet{Genest}

>>>>

However, the test is often misused. The standard one-sample K-S test applies to 
independent, continuous data with a hypothesized distribution that is completely specified. 
Often in literature, it has been "discovered" that the test loses its power when 
applied to dependent or discrete data with hypothesized distributions containing 
estimated parameters. In the case of estimated parameters, \citet{Steinskog} 
demonstrates the change in power when using estimated parameters and stress caution in 
using the K-S test in such ways. \citet{Lilliefors} shows 
that using the standard table when values of the mean and standard deviation are 
estimated obtains extremely conservative results. This is supported by \citet{Capasso}, which 
concludes that failing to re-estimate the parameters may lead to wrong, overly-conservative 
approximations to the distributions of goodness-of-fit test statistics based on the empirical 
distribution function. \citet{Capasso} also notes that the impact of this possible mistake 
may turn out to be dramatic and does not vanish as the sample size increases. Remedies are provided 
by \citet{Genest} and \citet{Babu} in the form of bootstrap. \citet{Genest} provides validity 
for using parametric bootstrap with various goodness-of-fit tests. \citet{Babu} details 
the bootstrap procedure for goodness-of-fit tests and notes that both parametric and 
non-parametric procedures lead to correct asymptotic levels, however there is a correction 
required for the non-parametric case. In the case of dependent data, \citet{Durilleul} demonstrates 
that the K-S statistic is too liberal for medium-to-high positive autocorrelation values. 
\citet{Durilleul} also shows that for negative autocorrelation values, the behavior is 
asymmettrical with respect to positive values. For remedies, \citet{Weiss} provides a 
procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) process 
where the parameters are known. \citet{Lanzante} tests various strategies for dealing with temporal dependence
and concludes that a test based on Monte-Carlo simulations performed the best.

The purpose of this paper is to expand on the misuses of the K-S test and propose 
solutions in the case that the K-S test would still like to be used. In order to set 
up the demonstrations, simulated data is used throughout. Unless otherwise specified, 
the random data is generated from a standard normal distribution with sample size $n = 100$. 
Therefore the cumulative distribution $F(x)$ of the K-S test for much of this paper is standard normal.

@@

The K-S test shows significant issues in the case of fitted parameters. One assumption 
of the K-S test is that the hypothesized distribution is completely specified. 
However, the procedure is sometimes performed where the population cumulative 
distribution $F(x)$ has parameters $\mu=\Xbar$, the sample mean, and $\sigma^2=s^2$, 
the sample variance \citep{Lilliefors}. This case is demonstrated in Figure~\ref{fig:hist_fitted} 
under the Naive plot. The naive K-S test was performed by estimating the parameters 
of $F(x)$ using the fitted distribution of the sample data. Since the data is generated 
from a standard normal distribution with seemingly all assumptions met, a uniform 
distribution of $U(0,1)$ is expected for the p-values. However this is under the 
assumption that the K-S test holds its power, which it no longer does due to using 
fitted parameters. Therefore, there is notable deviation from the uniform distribution.

To resolve this problem, both parametric and non-parametric bootstrap can be performed. 
Performing bootstrap onto goodness-of-fit tests such as the K-S test is a well-researched 
topic.

@@

\citet{Weiss}
\citet{Arnold}
\citet{Conover}
\citet{Gleser}
\citet{Butorina}
\citet{Racine}
\citet{Wang}
\citet{Dimitrova}
